D-Hammer: Efficient Equational Reasoning for Labelled Dirac Notation

### 2025-01-31 02language_design.tex
.

\begin{lemma}[Soundness of type system]
    For any well-formed context \( E \), term \( t \), and type \( T \), if \( E \vdash t : T \), then for all valuations \( v \), \( \sem{t}_v \in \sem{T}_v \).
\end{lemma}
\begin{proof}
By induction on the derivation.
\end{proof}
This interpretation formalizes the standard understanding of Dirac
notation and provides the foundation for the algorithm. However,
computers cannot directly reason about equivalence through
mathematical interpretations. We proceed by defining a proof system
that abstracts these concepts.

>>>>

\begin{lemma}[Soundness of type system]
  If \( E \vdash t : T \), then for all valuations \( v \) valid w.r.t.\,
  $\Gamma$, we have \( \sem{t}_v \in \sem{T}_v \).
\end{lemma}
\begin{proof}
By induction on the derivation.
\end{proof}
This interpretation formalizes the standard understanding of Dirac
notation and provides the foundation for the algorithm. However,
computers cannot directly reason about equivalence through
mathematical interpretations. We proceed by defining a proof system
that abstracts these concepts.
